\begin{recipe}{\texorpdfstring{$\star$}{str}Aloo Gobi}{6 servings - 202 calories}{}

\freeform From Indian Healthy Recipes by Swasthi.

\Ing{510 g (2 \nicefrac{1}{4} cups) cubed potato}
\Ing{450 g (4 \nicefrac{1}{2} cups) cauliflower florets}
\Ing{1 tbsp oil}
\Ing{1 \nicefrac{1}{2} tsp cumin seeds}
\Ing{3 cups coarsely chopped onion}
\Ing{1 green chili (or more to taste)}
\Ing{2 \nicefrac{1}{4} cups seeded cubed tomatoes}
\Ing{3 tsp ginger garlic paste}
\Ing{18-24 cashews or 6-9 tbsp cream}
\Ing{2 \nicefrac{1}{4} garam masala}
\Ing{2 \nicefrac{1}{4} coriander powder}
\Ing{2 \nicefrac{1}{4} Kashmiri red chili powder (more or less to taste)}
\Ing{Salt, to taste}
\Ing{1 \nicefrac{1}{2} tsp dried fenugreek leaves (kasuri methi)}
\Ing{Cilantro (coriander leaves), for garnish}

Chop onions to cubes and blend them into a paste. Seed the tomatoes and cube them as well. Add them to a blender jar with the cashews and
blend them into a creamy paste.\\

Steam or boil potatoes and cauliflower until half cooked. Bring 2 cups water to a boil in a cooker or steamer. Add the cubed potatoes (aloo) to a steam basket and steam them until half done. Then add cauliflower (gobi) to the same basket and steam until al dente. Set these aside. For a restaurant style, you can skip steaming and shallow fry these until half cooked and aromatic. Set these aside.\\

Heat a pan with oil, add cumin and allow to splutter. Add ginger garlic paste and saute until the raw smell goes away. Add the onion paste and cook until the paste turns light golden brown and the raw smell goes away. Add tomato paste and cook until the masala turns thick and evaporates all the moisture.\\

Add chili, garam masala, coriander powder, red chili powder and salt. Saute until the masala begins to leave the sides of the pan.\\

Add 2 \nicefrac{1}{2} cups of water. You can also use the steamed stock. Let the gravy begin to bubble and thicken a bit.

Add the half cooked aloo gobi to the gravy. Cover and simmer until the veggies are cooked completely. Add kasuri meti. Switch off. Add coriander leaves and serve.

\end{recipe}