\begin{recipe}{$\star$Punjabi-Style Black Lentils}{6 servings - 260 calories}{}

\freeform From Smitten Kitchen. (+ 108 cal for \nicefrac{1}{2} cup cooked brown rice).

\Ing{\textbf{Dal}}
\Ing{2 tablespoons oil, butter (regular or ghee)}
\Ing{1 large onion, finely chopped}
\Ing{\nicefrac{3}{4} teaspoon cumin seeds}
\Ing{1.5-inch piece of ginger, finely chopped}
\Ing{3 garlic cloves, finely chopped}
\Ing{1\nicefrac{1}{2} teaspoon ground coriander}
\Ing{\nicefrac{1}{2} teaspoon ground turmeric}
\Ing{\nicefrac{3}{4} teaspoon garam masala}
\Ing{Ground chile powder (such as Kashmiri), to taste}
\Ing{1\nicefrac{1}{2} cup finely chopped or pureed tomatoes, fresh or from a can}
\Ing{1\nicefrac{1}{2} teaspoon fine sea salt, plus more to taste}
\Ing{1\nicefrac{1}{2} cup dried black lentils (urad dal)}
\Ing{6\nicefrac{3}{4} cups water, plus more to taste\\}
\Ing{\textbf{To Finish (Optional)}}
\Ing{6 teaspoons butter (salted is lovely here)}
\Ing{3 tablespoons heavy cream}
\Ing{Handful chopped fresh cilantro}

Heat oil (or oil and butter) over medium. Once hot, add onion and cumin seeds and cook, stirring occasionally, until onion browned in spots. Add garlic and ginger, cook for 1 minute more, then the rest of the spices and tomato and cook for 3 minutes more, scraping up any stuck bits. Add water and salt, then lentils. Bring to simmer, then reduce to low and cover and cook until lentils are tender, between 35 and 45 minutes, stirring occasionally. For a looser dal, you can add more water. Adjust spices and seasonings to taste.\\

To finish, ladle into four bowls. Place a 1-teaspoon pat of butter in the center of each, letting it begin to melt before swirling in 1 1/2 teaspoons cream and finishing with cilantro.


\end{recipe}