\begin{recipe}{Black Bean Soup with Toasted Cumin Seed Crema}{6 servings - 321 calories}{}

\freeform From Smitten Kitchen. Can make ahead; keeps great in the fridge.

\Ing{\textbf{Soup}}
\Ing{1 tablespoon olive oil}
\Ing{2 medium-size red onions, chopped}
\Ing{1 medium-size red bell pepper, chopped}
\Ing{1 medium-size green bell pepper, chopped}
\Ing{4 garlic cloves, minced}
\Ing{4 teaspoons ground cumin}
\Ing{1 16-ounce package dried black beans}
\Ing{1 tablespoon chopped chipotle chiles from a can (this gives it a solid kick, dial back if you are wary)}
\Ing{7 cups hot water (can use very hot tap water)}
\Ing{2 tablespoons fresh lime juice}
\Ing{2 teaspoons coarse kosher salt}
\Ing{\nicefrac{1}{4} teaspoon ground black pepper\\}
\Ing{\textbf{Crema} (+138 cal)}
\Ing{1 tablespoon whole cumin seeds}
\Ing{1 cup crema or crème fraîche (or swap sour cream or yogurt, for a close-enough taste)}
\Ing{Salt and freshly ground pepper}

\textbf{Black Bean Soup}

Heat olive oil in large skillet (slow cooked) or large pot (stove top) over medium-high heat. Add onions and both bell peppers and sauté until beginning to brown, about eight minutes. Add garlic and cumin; stir one minute.\\

\textit{Slow Cooker}

Transfer mixture to 6-quart slow cooker. Add beans and chipotles, then 7 cups hot water. Cover and cook on high until beans are very tender, about 3 hours (or longer if they are not ready).\\

\textit{Stove Top}

Add beans and chipotles, then 7 cups water. Bring to a full boil, boil for 1 minute, then reduce heat to a gentle simmer, partially cover pot, and cook until beans have softened, about 2 to 3 hours. (These times can vary a lot depending on the age of the beans and kind of water.)\\

\textit{Once Cooked}

Transfer two cups bean mixture to blender; puree until smooth. Return puree to remaining soup in slow cooker or pot. Stir in lime juice, salt, and pepper. Adjust seasonings to taste. Ladle soup into bowls. Spoon dollop of toasted cumin seed cream (below) over each bowl and serve.\\

\textbf{Toasted Cumin Seed Crema}

Place the cumin in a small sauté pan over medium heat. Toast until lightly golden brown. Place in spice grinder or mortar and pestle and grind until coarse. Stir it into the crema and season with salt and pepper, to taste.

\end{recipe}