\begin{recipe}{\texorpdfstring{$\star$}{str}Marinated Cauliflower Steaks with Chilli Quinoa}{4 servings - 386 calories}{}

\freeform From {\normalfont Deliciously Ella with Friends} by Ella Woodward (p. 134).

\Ing{\textbf{Cauliflower Steaks}}
\Ing{2 cauliflower heads, cut into 4 thick `steaks'}
\Ing{\nicefrac{1}{2} tsp ground turmeric}
\Ing{2 tsp ground cumin}
\Ing{2 tsp paprika}
\Ing{\nicefrac{1}{2} tsp chile powder}
\Ing{50 ml olive oil}
\Ing{Salt and pepper}
\Ing{\nicefrac{1}{2} lemon, juiced\\}
\Ing{\textbf{Chilli Quinoa}}
\Ing{200 g quinoa}
\Ing{20 g cilantro}
\Ing{1 red chile, deseeded and finely chopped}
\Ing{1 avocado}
\Ing{3 tbsp olive oil}
\Ing{2 tbsp apple cider vinegar}
\Ing{\nicefrac{1}{2} lemon, juiced}
\Ing{1 tbsp toasted sesame oil}
\Ing{1 tbsp tamari}
\Ing{\nicefrac{1}{2} tsp chile powder}
\Ing{100 g spinach\\}
\Ing{\textbf{Toppings (Optional)}}
\Ing{Hummus}

Place the cauliflower steaks in a single layer on a large baking tray. Whisk all the remaining cauliflower ingredients together in a bowl, with 25 ml of water, to make a dressing. Pour this over the cauliflower and turn to make sure each steak is evenly coated. Leave to marinate for at least 1 hour.\\

Preheat the oven to 180\textdegree C (350\textdegree F). Roast for about 40 minutes until tender, turning every so often.\\

Meanwhile, make the quinoa. Place the quinoa into a saucepan with 450 ml of water and a little salt. Place the lid on and bring it to the boil, then reduce the heat to a simmer. Cook for 12-15 minutes.\\

Mix the cilantro and chile. Peel and pit the avocado, mash the flesh, then mix it with the cilantro and chile, the olive oil, vinegar, lemon juice, sesame oil, and tamari. Season well and stir in the chile powder. Once the quinoa is cooked, stir in the spinach so that it wilts a little, then stir in the avocado mixture.\\

Place each cauliflower steak on a bed of quinoa and add a big dollop of hummus (optional).

\end{recipe}