\begin{recipe}{\texorpdfstring{$\star$}{str}Ceasar Salad with Creamy Roasted Garlic Dressing}{6 servings - 126 calories}{}

\freeform From {\normalfont More HeartSmart Cooking} by Bonnie Stern (p. 79).

\Ing{\textbf{Dressing}}
\Ing{1 head roasted garlic}
\Ing{1 tsp Dijon mustard}
\Ing{1 tsp Worcestershire sauce}
\Ing{2 tbs red wine vinegar}
\Ing{2 tbs olive oil}
\Ing{\nicefrac{1}{3} cup low-fat yogurt}
\Ing{\nicefrac{1}{4} cup grated Parmesan cheese}
\Ing{Salt and pepper to taste\\}
\Ing{\textbf{Salad}}
\Ing{3 slices crusty whole wheat bread, cut into 1-in cubes}
\Ing{1 large head romaine lettuce, torn up}

To roast garlic, trim about \nicefrac{1}{4}-in off the top of the garlic head. Remove any of the parchment-like skin that comes off easy. Place garlic in a baking dish, cut side up and drizzle lightly with olive oil. Cover with a foil and bake at 300$\degree$F for 1\nicefrac{1}{2} hours. Remove foil and bake for 20 minutes longer. The garlic should be very tender. Remove garlic by gently squeezing it out of the skins.\\

\textbf{Creamy Roasted Garlic Dressing}

In a food processor or blender, blend together roasted garlic, mustard, Worcestershire sauce, vinegar, oil, yogurt, and Parmesan. Taste and season with salt and pepper. Refrigerate until ready to use.\\

\textbf{Croutons}

Spread bread crumbs on baking sheet. Bake at 375$\degree$F for 10 to 12 minutes, or until crunchy. Stir once or twice during baking time.\\

\textbf{Salad}

Just before serving, toss lettuce with desired amount of dressing and top with croutons. If you want, garnish with tomatoes.

\end{recipe}