\begin{recipe}{Chocolate Oblivion Truffle Torte}{16 slices - 260 calories ea.}{}

\freeform From 101 Cookbooks. Can be kept for 2 weeks in the fridge. Do not freeze.

\Ing{454 g 70\% bittersweet chocolate (this cake really highlights the chocolate, so use the good stuff)}
\Ing{227 g unsalted butter}
\Ing{6 large eggs (about 340 g with shells)}
\Ing{3 tablespoons superfine sugar (adjust sugar based on chocolate used)}

All ingredients should be at room temperature.\\

Prepare one 8-inch springform pan at least 2 1/2 inches high, buttered and bottom lined with buttered parchment or wax paper; outside of pan wrapped with a double layer of heavy-duly foil to prevent seepage. You will also need one 10-inch cake pan or roasting pan to serve as a water bath.\\

Preheat the oven to 425$\degree$F.\\

In large metal bowl set over a pan of hot, not simmering, water (the bottom of the bowl should not touch the water) combine the chocolate and butter and let stand, stirring occasionally, until smooth and melted. (The mixture can be melted in the microwave on high power, stirring every 15 seconds. Remove when there are still a few lumps of chocolate and stir until fully melted.)\\

In a large bowl set over a pan of simmering water heat the eggs, stirring constantly to prevent curdling, until just warm to the touch. Remove from the heat, add the sugar, and beat, using the whisk beater, until triple in volume and soft peaks form when the beater is raised, about 5 minutes. (To insure maximum volume if using a hand mixer, beat the eggs over simmering water until they are hot to the touch, about 5 minutes. Remove from the heat and beat until cool.)\newpage

Using a large wire whisk or rubber spatula, fold \nicefrac{1}{2} the eggs into the chocolate mixture until almost incorporated. Fold in the remaining eggs until just blended and no streaks remain. Finish by using a rubber spatula to ensure that the heavier mixture at the bottom is incorporated. Scrape into the prepared pan and smooth with the spatula. Set the pan in the larger pan and surround it with 1 inch very hot water. Bake 5 minutes. Cover loosely with a piece of buttered foil and bake 10 minutes. (The cake will look soft, but this is as it should be.)\\

Let the cake cool on a rack 45 minutes. Cover with plastic wrap and refrigerate until very firm, about 3 hours.\\

To unmold, have ready a serving plate and a flat plate at least 8 inches in diameter, covered with plastic wrap. Wipe the sides of the pan with a hot, damp towel.\\

Run a thin metal spatula around the sides of the cake and release the sides of the springform pan. Place the plastic-wrapped plate on top and invert. Wipe the bottom of the pan with a hot, damp towel. Remove the bottom of the pan and the parchment. Reinvert onto the serving plate.\\

Serve at room temperature (not chilled!). Cut into narrow wedges with a thin sharp knife that has been dipped in hot water.\\

\textbf{Notes}

For a moist airy texture, be sure to add beaten eggs to chocolate mixture and not the chocolate to the eggs. Wrapping the pan with foil keeps it watertight. Chill thoroughly before unmolding. Use the plastic-wrapped plate when unmolding to protect the surface of cake if you're not planning to use a topping.

\end{recipe}