\begin{recipe}{Crispy Potato Hash}{4 servings - 383 calories}{}

\freeform From Serious Eats.

\Ing{1 \nicefrac{1}{2} pounds (680 g) russet or Yukon gold potatoes, cut into \nicefrac{3}{4}- to \nicefrac{1}{2}-inch dice}
\Ing{2 tablespoons distilled white vinegar}
\Ing{Kosher salt}
\Ing{\nicefrac{1}{4} cup vegetable, canola, or olive oil, divided, plus more as needed}
\Ing{\nicefrac{1}{2} teaspoon ground cumin}
\Ing{\nicefrac{1}{4} teaspoon ground paprika}
\Ing{Freshly ground black pepper}
\Ing{6 green onions, white and light green parts sliced, greens parts reserved separately}
\Ing{1 bell or poblano pepper, cut into \nicefrac{1}{2}-inch dice}
\Ing{4 eggs}
\Ing{\nicefrac{1}{4} cup roughly chopped fresh parsley or cilantro leaves}
\Ing{\nicefrac{1}{2} small avocado diced}
\Ing{homemade or store-bought salsa, for serving}

Place potatoes in a large saucepan and cover with 2 quarts cold water. Add vinegar and 2 tablespoons kosher salt. Bring to a boil over high heat. Reduce to a simmer and cook until barely tender, about 5 minutes after coming to a boil. Drain potatoes in a colander and let drain for 2 minutes. If finishing in the oven, preheat to 375$\degree$F.\\

When potatoes are drained, add 3 tablespoons oil to skillet and heat over medium-high heat until shimmering. Add drained potatoes and cook, stirring and tossing occasionally, until potatoes are deep brown and crisp on all sides, about 20 minutes total. Add cumin and paprika and cook, stirring, until fragrant, about 30 seconds. Season to taste with salt and pepper. Transfer potatoes to bowl and set aside.\\

Add remaining tablespoon oil to skillet and heat over high heat until shimmering. Add green onion whites and light greens and pepper and cook, stirring occasionally, until charred, about 2 minutes. Season to taste with salt and pepper then transfer to bowl with potatoes. Toss contents of bowl and either fry up 4 eggs and serve, or return to skillet and make 4 wells in potato mixture.\\

Carefully break 1 egg into a small bowl and slide into a fine mesh strainer over the sink. Swirl egg very gently until excess loose white drains away. Carefully add to one of the cavities in the skillet. Repeat with remaining three eggs.\\

Drizzly eggs with a few drops of oil, season with salt and pepper, and transfer to oven. Cook until whites are barely set but yolks are still runny, about 10 minutes. Remove from oven, garnish with remaining green onions, chopped parsley or cilantro, and avocado. Serve immediately with salsa.\\

%\textbf{Notes}

%Feel free to fry the eggs separately instead of baking them into the hash.

\end{recipe}