\begin{recipe}{\texorpdfstring{$\star$}{str}Curried Tomato Tortellini Soup}{4 servings - 408 calories}{}

\freeform From 101 Cookbooks.

\Ing{4 big handfuls spinach, chopped (or frozen equivalent)}
\Ing{2 tbsp extra virgin olive oil}
\Ing{1 medium yellow onion, diced}
\Ing{3 cloves garlic, minced}
\Ing{2 \nicefrac{1}{2} tsp curry powder}
\Ing{\nicefrac{3}{4} tsp sweet (or smoked) paprika}
\Ing{\nicefrac{1}{2} tsp ground turmeric}
\Ing{\nicefrac{3}{4} tsp red chilli flakes}
\Ing{1 28- ounce can whole tomatoes, with liquid}
\Ing{\nicefrac{3}{4} cup dried red lentils, rinsed}
\Ing{4 cups water}
\Ing{1 tsp fine grain sea salt, plus more to taste}
\Ing{\nicefrac{1}{2} pound fresh tortellini}
\Ing{to serve: a bit of grated cheese, lemon (optional)}

If you're using frozen spinach, set it on the counter to thaw a bit. In the meantime, heat the olive oil in a large pot over medium-high heat. Stir in the onion and cook, stirring occasionally, for 5 minutes or so, until the onion has softened a bit. Stir in the garlic, wait a minute, then add the curry powder, paprika, turmeric, and chilli flakes, and stir well.\\

Break up the tomatoes with your hands as you add them to the pot along with the tomato liquid, stir in the lentils, and the water. Cover and allow to cook for 15 minutes or so, until the lentils have cooked through. Stir in the salt, and then the tortellini. Cover and cook for another 3-5 minutes, or per package instructions - until tender and cooked through. Stir in the spinach bring back to a simmer, and serve with a dusting of cheese and a squeeze of lemon juice. If you need to thin out with a bit more water, do so, and re-season. Enjoy!\\

\end{recipe}