\begin{recipe}{\texorpdfstring{$\star$}{str}Dal Makhani}{6 servings - 343 calories}{}

\freeform From Indian Healthy Recipes by Swasthi.

\Ing{1\nicefrac{1}{2} cups black lentils (urad dal)}
\Ing{\nicefrac{1}{2} cups red kidney beans (rajma)}
\Ing{~9 cups water}
\Ing{1 small Indian bay leaf (tej patta)}
\Ing{3 tbsp ghee, butter, or oil}
\Ing{3 medium onions}
\Ing{2\nicefrac{1}{4} cups tomato puree or 6 medium tomatoes seeded and cut finely}
\Ing{4\nicefrac{1}{2} tsp ginger garlic paste (p.\pageref{components:gingergarlicpaste})}
\Ing{1-3 green chilies sliced open}
\Ing{\nicefrac{1}{4} heaping tsp asafoetida (hing, optional)}
\Ing{9-12 tbsp cream}
\Ing{\nicefrac{3}{4} tsp dried fenugreek leaves (kasuri methi, optional)}
\Ing{3-4\nicefrac{1}{2} cups water}
\Ing{\textbf{Whole spices:}}
\Ing{1\nicefrac{1}{2} cumin seeds (jeera)}
\Ing{6 green cardamom pods}
\Ing{1 cinnamon stick (about 1.5 in long)}
\Ing{6 whole cloves}
\Ing{3 small black cardamom pods}
\Ing{\textbf{Spice mix:}}
\Ing{\nicefrac{3}{4} tsp turmeric powder}
\Ing{1\nicefrac{1}{2} Kashmiri chili powder}
\Ing{1\nicefrac{1}{2} garam masala}
\Ing{3 tsp coriander powder}
\Ing{Salt to taste}

Wash urad dal and rajma together several times and soak overnight. Drain and rinse and add them to a pot. Also add bay leaf. Pour in 9 cups of water and cook until very soft (should be easy to mash with a fork), adding water when needed.\\

Heat a heavy bottom pot with butter or oil. Add all whole spices - cumin, cardamoms, cloves and cinnamon. All spices are optional except cumin. Allow to crackle. Then add hing, ginger garlic paste and green chilies. Saute until aromatic. Next throw in the onions and fry until they turn golden. Then transfer tomato puree, turmeric, chili powder, garam masala, coriander powder (optional) and salt. Saute well until the masala leaves the pan. Pour in the cooked dal along with their stock.\\

Stir well and begin to cook on a low fame stirring often. You will need to add half cup water each time the dal thickens. Stir and continue to cook on the lowest possible heat. You can use about 1 to 2 cups water and simmer for 60 to 90 mins on a very low fame or as long as 4 to 6 hours for a more aythetic taste. Remember to keep stirring and add water whenever needed. Once it is thick and creamy, you can add cream and turn off. It tastes good even without the addition of cream. If having it the next day or later, you can refrigerate. Heat up when ever needed by adding little water. When it comes to a boil, add cream and stir well. Dal Makhani can be served with butter topped and garnished with coriander and ginger Juliennes. Dal makhani tastes best the next day. So you may refrigerate and have it the next day. Serve dal makhani with plain rice, naan or roti.\\

\end{recipe}