\begin{recipe}{\texorpdfstring{$\star$}{str}Focaccia}{36 pieces}{}

    \Ing{7 g instant yeast}
    \Ing{2 tbsp kosher salt}
    \Ing{3 cups warm water \\($\sim43 \degree$C, $ \sim110 \degree$F)}
    \Ing{780g bread flour}
    \Ing{$\nicefrac{3}{4}$ cup extra-virgin olive oil}
    \Ing{Flaky salt}
    \Ing{Fresh rosemary}


    \textbf{Making the dough}: Combine water and yeast, let sit for 5 minutes. Add flour and kosher salt. Using a stand mixer with the dough hook attachment, mix on lowest setting to combine. Once combined, mix on med-high for 5 minutes. Let rest under a damp towel in the mixer for 10 minutes. Remove towel and continue mixing on med-high for 15 minutes. \\

    \textbf{First rest of the dough}: Add $\nicefrac{1}{4}$ cup of EVOO to a large bowl. Add dough to bowl and cover with damp towel for at least 1 hour, or until doubled in volume. \\

    \textbf{Second rest of the dough}: Add $\nicefrac{1}{4}$ cup of EVOO to a large sheet pan. Lift and fold dough at least 4 times in it's bowl, then place in sheet pan. Spread out, and let rest for 10 minutes if it doesn't reach the corners of the pan. Cover with an inverted sheet pan for 45 minutes or until it reaches the height of the pan. \\

    \textbf{Cooking the dough}: Dock the dough with oiled fingertips, breaking up and large bubbles that have formed. Spread out remaining $\nicefrac{1}{4}$ cup of EVOO over the dough, and place all desired toppings (fresh rosemary and flaky salt is great). Bake at $450\degree$F on bottom rack for 20-25 minutes, move to top rack for $\sim5$ minutes to crisp top of necessary. Let cool 5 minutes before removing from sheet pan.
\end{recipe}