\begin{recipe}{Grandfather’s Pasta}{4 servings - 733 calories}{}

\freeform From La Tartine Gourmade.

\Ing{2 lb tomatoes (6 medium-sized tomatoes)}
\Ing{2 Tbsp olive oil}
\Ing{3.5 oz red onion, sliced thinly}
\Ing{2 garlic cloves, crushed}
\Ing{1 Tbsp sun-dried tomato paste}
\Ing{A few sun dried tomatoes in oil (about 5)}
\Ing{Salt and pepper}
\Ing{1 Tbsp whole cane sugar}
\Ing{Nice Bunch of fresh thyme}
\Ing{\nicefrac{1}{4} cup dry white wine}
\Ing{1 cup fresh whole milk ricotta}
\Ing{Fresh basil}
\Ing{1 Espelette pepper (optional)\\}
\Ing{14 oz pasta, tagliatelle, linguini or spaghetti}

Boil the tomatoes for 1 min and rinse them under cold water. Peel and seed them. Dice them.\\

Heat 3 Tbsp olive oil in a sauté pan and when hot, add the crushed garlic and sliced onions. Cook for a few min without browning.\\

Add the tomato paste and cook for 1 min until well coated, stirring constantly.
Add the tomato pieces and diced dried tomatoes. Mix and season with salt and pepper, and add the sugar. Cook on medium to low heat for 2 to 3 min.\\

Add the thyme twigs and pour the white wine. Cook uncovered for about 20 min, on low to medium heat. Keep an eye so that you does not stick to the bottom.
Remove from the heat and purée in a food processor.\\

Add the ricotta and continue to mix to obtain a nice grainy cream. Check the seasoning and add freshly chopped basil.\\

Cook your pasta following the instructions on your package and coat them with the sauce. Add more basil and optionally, some piment d’Espelette.

\end{recipe}