\begin{recipe}{Green Lentil Soup with Curried Brown Butter and Paneer}{6 servings - 492 calories}{}

\freeform From 101 Cookbooks.

\Ing{2 tbsp unsalted butter, ghee, or extra-virgin coconut oil}
\Ing{1 large yellow onion, chopped}
\Ing{3 cloves garlic, chopped}
\Ing{\nicefrac{1}{2} tsp red pepper flakes}
\Ing{5\nicefrac{1}{2} cups vegetable broth or water}
\Ing{1\nicefrac{1}{2} (300 g) green lentils or green split peas, picked over and rinsed}
\Ing{3 tbsp unsalted butter}
\Ing{1 tbsp Indian curry powder}
\Ing{\nicefrac{1}{2} cup coconut milk}
\Ing{Fine-grain sea salt}
\Ing{1 bunch fresh chives, minced}
\Ing{1 package paneer, cut into small cubes and pan-fried}

Combine the 2 tablespoons butter, onion, garlic, and red pepper flakes in a large soup pot over medium heat, stirring regularly, until the onions soften, a couple minutes. Add the vegetable broth and lentils and simmer, covered, until the lentils are tender. This usually takes 20 to 30 minutes, but can take as long as 50 minutes.\\

In the meantime, warm the 3 tablespoons butter in a small saucepan over medium heat and let it brown. When it starts to smell nutty and fragrant, stir in the curry powder and sauté until the spices are fragrant, less than a minute. When the lentils are finished cooking, remove from the heat, stir in the coconut milk and \nicefrac{1}{4} teaspoon salt, and puree with an immersion blender. You can leave the soup a bit chunky if you like, or puree until it is perfectly smooth.\\

Stir in half of the spiced butter, taste, and add more salt, if needed, typically a couple of teaspoons if you used water instead of a salted broth. Serve drizzled with the remaining spice butter and sprinkled with chives and paneer cubes.
\end{recipe}