\begin{recipe}{Classic Grilled Cheese with Cream of Tomato Soup}{4 servings - 737 calories}

\freeform From Smitten Kitchen.

\Ing{\textbf{Soup}}
\Ing{2 (28-ounce) cans whole tomatoes packed in juice, drained, 3 cups juice reserved}
\Ing{1 \nicefrac{1}{2} tablespoons dark brown sugar}
\Ing{4 tbsp unsalted butter}
\Ing{4 large shallots, minced (about \nicefrac{1}{2} cup)}
\Ing{1 tbsp tomato paste}
\Ing{Pinch ground allspice}
\Ing{2 tbsp all-purpose flour}
\Ing{1 \nicefrac{3}{4} cups chicken stock, homemade or canned low-sodium}
\Ing{\nicefrac{1}{2} cup heavy cream}
\Ing{2 tbsp brandy or dry sherry}
\Ing{Salt and cayenne pepper\\}
\Ing{\textbf{Sandwiches}}
\Ing{6 ounces cheese (preferably mild cheddar) or combination of cheese, grated on large holes of box grater (about 1\nicefrac{1}{2} cup)}
\Ing{8 slices (1/2 inch-thick) from white sandwich bread}
\Ing{4 tbsp butter (preferably salted), melted}

\textbf{Cream of Tomato Soup}

Adjust oven rack to upper-middle position and heat oven to 450°F. Lined rimmed baking sheet with foil. With fingers, carefully open whole tomatoes over strainer set in bowl and push out seeds, allowing juices to fall through strainer into bowl. Spread seeded tomatoes in single layer on foil. Sprinkle evenly with brown sugar. Bake until all liquid has evaporated and tomatoes begin to color, about 30 minutes. Let tomatoes cool slightly, then peel them off foil; transfer to small bowl and set aside.\\

Heat butter over medium heat in large saucepan until foaming. Add shallots, tomato paste and allspice. Reduce heat to low, cover, and cook, stirring occasionally, until shallots are softened, 7 to 10 minutes. Add flour and cook, stirring constantly, until thoroughly combined, about 30 seconds. Gradually add chicken stock, whisking constantly to combine; stir in reserved tomato juice and roasted tomatoes. Cover, increase heat to medium, and bring to a boil. Reduce heat to low and simmer, stirring occasionally, to blend flavors, about 10 minutes.\newpage

Pour mixture through strainer and into medium bowl; rinse out saucepan. Transfer tomatoes and solids in strainer to blender; add 1 cup strained liquid and puree until smooth. Place pureed mixture and remaining strained liquid in saucepan. Add cream and warm over low heat until hot, about 3 minutes. Off heat, stir in brandy and season with salt and cayenne. Serve immediately. (Soup can be refrigerated in an airtight container for up to 2 days. Warm over low heat until hot; do not boil.)\\

\textbf{Grilled Cheese Sandwiches}

Heat heavy 12-inch skillet over low to medium-low heat. Meanwhile, sprinkle a portion of cheese over two bread slices. Top each with a remaining bread slice, pressing down gently to set.\\

Brush sandwich tops completely with half of melted butter; place each sandwich, buttered-size down, in skillet. Brush remaining side of each sandwich completely with remaining butter. Cook until crisp and deep golden brown, 5 to 10 minutes per side, flipping sandwiches back to first side to reheat and crisp, about 15 seconds. Serve immediately.

\end{recipe}