\begin{recipe}{Imperial Macaroni Bake}{6 servings - 500 calories}{}

\freeform From {\normalfont The New Chatelaine Cookbook} by Monda Rosenberg (p.177).

\Ing{3-5 cups elbow macaroni}
\Ing{\nicefrac{1}{4} cup butter}
\Ing{\nicefrac{1}{4} cup all-purpose flour}
\Ing{3 cups milk}
\Ing{1 tsp Dijon mustard}
\Ing{\nicefrac{1}{2} tsp salt}
\Ing{\nicefrac{1}{2} tsp white pepper}
\Ing{Pinch of freshly grated nutmeg}
\Ing{\nicefrac{1}{2}-lb (250 g) container MacLaren's Imperial Cold Pack Cheddar Cheese\\}
\Ing{\textbf{Topping (+167 cal)}}
\Ing{\nicefrac{1}{4} cup butter, melted}
\Ing{\nicefrac{1}{2} cup coarse dry bread crumbs}

Preheat oven to 350$\degree$F. Lightly grease a 10-cup (2.5 L) baking dish and set aside. Cook macaroni al dente and drain.\\

Meanwhile, melt \nicefrac{1}{4} cup butter in a heavy-bottomed saucepan set over medium-low heat. Stir in the flower until blended. Cook for about 2 minutes, stirring often. Gradually whisk in the milk, Dijon, salt, pepper, and nutmeg. Increase heat to medium. Stir the sauce until it comes to a boil and has thickened. Remove from the heat. Stir in spoonfuls of the cheese until blended. Cover, remove from the heat and set aside.\\

Make the topping by combining remaining \nicefrac{1}{4} cup melted butter and the bread crumbs. Set aside. Stir the cooked pasta into the cheese sauce until evenly mixed. Turn into the prepared baking dish. Sprinkle with the bread crumb topping.\\

Bake in the centre of the oven for 30 minutes or until the sauce around the sides of the dish is bubbly and the topping is golden. Let sit for 5 minutes before serving.

\end{recipe}