\begin{recipe}{Meyer Lemon Tarts}{8 tarts - 715 calories ea.}{}

\freeform From La Tartine Gourmande.

\Ing{\textbf{Sweet Crust}}
\Ing{1 \nicefrac{3}{4} cups all-purpose flour}
\Ing{1 egg}
\Ing{1 pinch of salt}
\Ing{1 oz almond flour}
\Ing{\nicefrac{2}{3} cup butter, soft}
\Ing{1 tbs confectioner’s sugar\\}
\Ing{\textbf{Lemon Cream}}
\Ing{5 Meyer lemons, zest and juice}
\Ing{4 eggs}
\Ing{227 g fine sugar}
\Ing{1 cup butter, at room temperature\\}
\Ing{\textbf{Lemon Peels}}
\Ing{Sugar}
\Ing{Water}
\Ing{2 Meyer lemons for the peels}

\textbf{Sweet Crust}

Sift the flour on a working area. Add the salt in the middle.\\

Add the soft butter and make a crumble with the dough, using the tips of your fingers.\\

Make a hole in the middle and add the confectioner’s sugar and almond flour. Then add the egg, working the dough with the tips of your fingers still. Make a ball with it and place it in plastic wrap. Put in the fridge for a minimum of 2 to 3 hours, if possible.\\

Roll your dough and place it in greased molds. Make little holes with a fork. Cover with pieces of parchment paper covered with weights, such as rice. Cook in the preheated oven at 350 F for about 20 minutes.\\

Remove the paper and continue to cook for about 5 to 6 minutes.\\

Remove from the oven and let cool on a cooling rack.\\

\textbf{Meyer Lemon Cream}

Place the sugar in a large bowl.\\

Grate finely the zest of the lemons and add them to the sugar. Mix with the tip of your fingers.\\

Add the eggs and lemon juice (about 6 oz or 3/4 cup) and whisk well.\\

Place the bowl over a pot of simmering water without touching, in order to thicken the cream. It is ready when it coats a wooden spoon.\newpage

Remove from the heat and let cool a little before adding the pieces of soft butter. Mix well by hand first until the butter is melted, then with a hand mixer to lighten the cream. It can take a few minutes.\\

\textbf{Candied Lemon Peels}

Boil the lemon sticks in water for 3 minutes, and repeat 3 times (change the water each time). Make a syrup with the same amount of water and sugar mixed together. Bring to a gentle boil and then add the lemon peels. Cook for about 10 to 15 minutes, on medium to low heat. Keep an eye on it to prevent burning as there is little liquid.\\

\textbf{Tarts}

Once the crusts are cold, fill them with lemon cream. Level it and add the candied peels on top. Let cool a little before serving.

\end{recipe}