\begin{recipe}{Mocha-Cream Roll}{10 servings - 322 calories}{}

\freeform From {\normalfont The Good Housekeeping Illustrated Cookbook} by Zoe Coulson (p. 391).

\Ing{5 eggs, separated, at room temperature}
\Ing{1 cup icing sugar}
\Ing{\nicefrac{1}{8} tsp. salt}
\Ing{1 tsp cocoa powder\\}
\Ing{\textbf{Mocha-Cream Filling}}
\Ing{1 \nicefrac{1}{2} cups heavy cream}
\Ing{\nicefrac{1}{2} cup cocoa powder}
\Ing{\nicefrac{1}{4} cups icing sugar}
\Ing{2 tbs. coffee liqueur\\}
\Ing{\textbf{Chocolate Icing}}
\Ing{3 oz semisweet chocolate}
\Ing{1 tbs. butter}
\Ing{1 tbs. light corn syrup}
\Ing{3 tbs. milk\\}
\Ing{\textbf{Glaze}}
\Ing{\nicefrac{1}{2} cup icing sugar}
\Ing{2-3 tsp. water}

Preheat oven to 400$\degree$F. Grease 15\nicefrac{1}{2} by 10\nicefrac{1}{2}-in jelly-roll pan; line bottom of pan with waxed paper; grease and flour paper.\\

In large bowl with mixer at high speed, beat egg whites until soft peaks form. Beating at high speed, gradually sprinkle icing sugar, beating thoroughly after each addition. Continue beating until the egg whites stand in stiff, glossy peaks. Set aside.\\

In small bowl with same beaters and with mixer at high speed, beat egg yolks until thick and lemon-coloured. Reduce speed to low: beat in salt, 1/2 cup icing sugar and 3 tablespoons cocoa powder, occasionally scraping bowl with rubber spatula. With wire wish or rubber spatula, gently fold yolk mixture into beaten whites just until the mixture is blended.\\

Spread batter evenly in pan and bake 15 minutes or until top springs back when lightly touched with finger. Prepare a clean cloth towel by sprinkling it with cocoa powder.\\

When cake is done, with small spatula, immediately loosen edges from side of pan; invert cake onto prepared towel. Gently peel waxed paper from bottom of cake. Roll towel with cake from narrow end, jelly-roll fashion. Cool completely, placing it seam side down, on wire rack.\newpage

\textbf{Mocha-Cream Filling}

As cake cools, in a medium bowl with mixer at medium speed, beat heavy cream, cocoa powder, icing sugar, and coffee liqueur until stiff peaks form.

When cake is cool, unroll from towel. Evenly spread Mocha-Cream Filling on cake almost to edges. Starting at the same narrow end, roll up cake without the towel this time. Place the cake, seam side down, on platter.\\

\textbf{Chocolate Icing}

In double broiler, over hot (not boiling!) water, melt semisweet chocolate with butter. Remove from heat; then beat in light corn syrup and milk until smooth. Spread icing over top and down sides of roll.\\

\textbf{Icing Sugar Glaze}

In a small bowl, stir in icing sugar and water until smooth. Drizzle the glaze over top of the roll to make a decorative design. Keep the roll in the refrigerator until you are ready to serve it.

\end{recipe}