\begin{recipe}{No Knead Bread}{1 loaf}{}

    \Ing{450 g [bread] flour}
    \Ing{2 tsp instant yeast}
    \Ing{2 tsp kosher salt}
    \Ing{375 ml warm water ($\sim43 \degree$C, $ \sim110 \degree$F)}

    \textbf{Making the Dough}: Mix water and yeast, let sit 5 min. Mix flour and salt in a large bowl. Add water and yeast mixture, then use a spatula to mix until all flour is incorporated. Dough will be wet and sloppy--not kneadable, but not runny like cake batter.\\

    \textbf{Rise}--Cover with a damp towel or plate for 2-3 hours, until it doubles in volume.
    \begin{itemize}
        \item Optional--refrigerate to develop a more complex flavour for 18 hours or up to 3 days
        \item Remove from fridge and leave at room temperature for 1 hour
    \end{itemize}

    \textbf{Preheat Oven} to $230\degree$C/$450\degree$F, put Dutch oven in oven with lid on. Once temperature is reached, wait a minimum of 30 minutes for Dutch oven to preheat.\\

    \textbf{Shape Dough}--While preheating the oven, sprinkle flour on your work surface. Scrape dough onto work surface, and fold sides of dough inwards at least 6 times, bursting bubbles in the dough and forming into a sphere. Transfer to parchment paper seam side down, and cover with bowl until oven is heated ($\sim 30$ minutes).\\

    \textbf{Transfer Dough}--cut slits in top of dough, transfer to dutch oven, place lid on. Bake 25 minutes covered, then 15 minutes uncovered.\\

    \textbf{Let cool} for at least 30 minutes.
\end{recipe}