\begin{recipe}{Quinoa Beet Veggie Burgers}{8 patties - 178 calories ea.}{}

\freeform From Minimalist Baker.

\Ing{\nicefrac{3}{4} cup cooked quinoa}
\Ing{\nicefrac{1}{2} large red onion, finely diced (about \nicefrac{3}{4} cup)}
\Ing{1 cup finely chopped mushrooms (shitake, baby bella, or white button)}
\Ing{pinch each salt \& pepper}
\Ing{1 15-ounce can black beans, well rinsed and drained}
\Ing{1 cup finely grated raw beet}
\Ing{1 tsp cumin}
\Ing{\nicefrac{1}{2} tsp chili powder}
\Ing{\nicefrac{1}{4} tsp smoked paprika}
\Ing{\nicefrac{1}{2} cup raw walnuts, crushed or ground into a loose meal}

Heat a large skillet over medium-low heat and add some nonstick spray or a bit of olive oil. Once hot add the onion and sauté, seasoning with a pinch each salt and pepper.\\

When the onions are soft – about 5 minutes – turn up the heat to medium and add the mushrooms. Season with another pinch of salt and pepper and cook until the mushrooms and onions are slightly browned and fragrant – about 3 minutes.\\

Remove from heat and add black beans and mash. You’re looking for a rough mash, so you can leave a bit of texture if you want.\\

Transfer the mixture to a mixing bowl and add the quinoa, beets, spices and stir. For even more flavor, add a shake of worcestershire or A-1 sauce (optional).\\

Lastly, add the walnut meal a little at a time until the mixture is able enough to form into patties. Set in the fridge to chill while your oven preheats to 375$\degree$F (190$\degree$C) (skip this step if cooking on the stovetop or grill).\\

Coat a baking sheet with nonstick spray or olive oil. Form mixture into roughly 8-9 patties. Use a peanut butter jar lid lined with plastic wrap to get the perfect shape. You can also just take handfuls and mash them into loose patties. The thicker you make them, the longer they’ll take to cook through, but the “juicier” and heartier they’ll be! Thinner patties will cook faster.\newpage

Arrange burgers on a baking sheet and brush or spray the tops with olive oil. Bake at 375$\degree$F (190$\degree$C) for a total of 30-45 minutes, gently flipping at the halfway mark. Cook longer to dry them out even more and achieve more crisp, but it’s not necessary.\\

Serve on small buns or atop mixed greens with desired toppings.\\

\textbf{Notes}

If you don’t want to cook the whole batch at once, form into 8 or 9 patties, par-bake them at 375 degrees F (190 C) for 15-20 minutes. Then cool and stack between layers of parchment paper and cover. Freeze for up to a few weeks. To cook, place on baking sheet still frozen and bake at 375 degrees F (190 C) until desired texture/color is reached - roughly 25-35 minutes.

\end{recipe}