\begin{recipe}{Roasted Butternut Squash Thanksgiving Sandwich}{4 sandwiches - 620 calories}{}

\freeform From Earthy Feast. Cranberry sauce from The Pig and Quill.

\Ing{\textbf{Caramelized Onions}}
\Ing{1 medium onion, chopped}
\Ing{1 tablespoon butter\\}
\Ing{\textbf{Super Savory Roasted Butternut Squash}}
\Ing{1 butternut squash}
\Ing{1 tablespoon of red miso paste}
\Ing{1 tablespoon honey}
\Ing{2 tablespoons of tamari}
\Ing{1 teaspoon of liquid smoke}
\Ing{3 to 4 tablespoons of olive oil}
\Ing{\nicefrac{1}{2} teaspoon garlic powder}
\Ing{a couple pinches of smoked ghost chili powder (or cayenne pepper)}
\Ing{a few sprigs of thyme, minced}
\Ing{1 sprig of rosemary, minced\\}
\Ing{\textbf{Cranberry Sauce}}
\Ing{4 oz fresh cranberries}
\Ing{2 tablespoons maple syrup divided}
\Ing{\nicefrac{2}{3} tablespoon olive oil}
\Ing{\nicefrac{1}{3} teaspoon chili powder}
\Ing{sea salt and black pepper\\}
\Ing{8 slices fresh sourdough bread}
\Ing{Dijon mustard}
\Ing{Mayo}

\textbf{Caramelized Onions}

Heat butter (or oil, or mix) in a pan on medium heat. Add onions and coat with butter. Cook on medium-low heat for 30 minutes to 1 hour, stirring occasionally to prevent onions from drying but not so often as to prevent them from browning. If the onions start to burn, reduce the heat. Continue to cook until the onions are a rich brown color. Optionally, deglaze pan with some balsamic vinegar.\\

\textbf{Butternut Squash Prep}

Peel and slice the butternut squash into half moons. Preheat oven to 400$\degree$F. Combine all the seasonings and spices into a large bowl. Rub the mixture onto the squash sliced to coat well. Place them on a parchment papered baking sheet.\\

\textbf{Cranberries Prep}

Toss cranberries with olive oil, \nicefrac{1}{2} tablespoon maple syrup, salt and pepper and arrange on a rimmed baking sheet in a single layer.\\

Roast both the butternut squash and the cranberries in the oven for 15-20 minutes or until the squash is tender and beginning to brown and the cranberries are burst and bubbling.\\

Mix roasted berries with chili powder, the rest of the maple syrup and another hefty pinch of salt.\\

Assemble the sandwiches on fresh sourdough bread with the squash, caramelized onions, cranberry sauce, dijon mustard, and mayo.

\end{recipe}