\begin{recipe}{$\star$Roasted Carrot and Avocado Salad with Crunchy Seeds}{4 servings - 268 calories}{}

\freeform From {\normalfont Food52 Genius Recipes} by Kristen Miglore (p 83).

\Ing{2 lbs (900 g) small carrots (3 in long and \nicefrac{1}{2} thick) or lage carrots, peeled quatered, and cut into 3 in segments}
\Ing{Kosher salt}
\Ing{1 orange, one half juiced, the other left whole}
\Ing{1 lemon, one half juiced, the other left whole}
\Ing{\nicefrac{1}{2} cut extra-virgin olive oil}
\Ing{1 tsp. cumin seeds}
\Ing{2 medium cloves garlic}
\Ing{1 tbs. fresh thyme leaves}
\Ing{1 tsp. red wine vinegar}
\Ing{1 tsp. crushed red pepper flakes}
\Ing{Freshly ground black pepper}
\Ing{1 tbs. sugar}
\Ing{1 avocado, peeled and cut in 12 wedges}
\Ing{2 cups mixed baby sprouts, herbs, and microgreens}
\Ing{\nicefrac{1}{4} cup crème fraîche}
\Ing{2 tbs. roasted sunflower seeds}
\Ing{2 tsp. toasted sesame seeds}

Preheat oven to 450$\degree$F with an oven rack in the centre.\\

Place the carrots in a saucepan and cover them with cold water. Season the water with a few pinched of salt, set the pan over high heat, and bring to a simmer. Reduce the heat to medium and simmer until the carrots are tender, about 10 minutes. Drain the carrots and transfer them to a rimmed baking sheet.\\

Combine 1 teaspoon each of the orange and the lemon juices, 2 tablespoons of olive oil, the cumin, garlic, thyme, vinegar, and red pepper flakes in a blender and blend until smooth. Season the marinade to taste with salt and pepper. Add the marinade and the unjuiced citrus halves to the carrots and toss with your hands until evenly combined. Roast until the carrots are slightly shriveled with a few brown spots, about 20 minutes, tossing occasionally with a spatula to brown them evenly. Allow the carrots to cool to room temperature.\\

Once they've cooled slightly, squeeze the juice from the roasted citrus halves into a small bowl. Add the remaining fresh citrus juices, remaining 6 tablespoons olive oil, and the sugar. Season the dressing to taste with salt and pepper and whisk to combine.\\

Divide the carrots and avocado slices among four plates and top with the greens. Add 1 tablespoon of crème fraîche to each salad. Sprinkle sunflower seeds and sesame seeds over each plate. Drizzle several tablespoons of the dressing over and around each salad (reserve any remaining dressing for later use) and serve immediately.

\end{recipe}