\begin{recipe}{\texorpdfstring{$\star$}{str}Saag Paneer}{6 portions - 300 calories}{}

\freeform From 101 Cookbooks.

\Ing{1\nicefrac{1}{2} pounds fresh (baby) spinach, well washed and dried (or frozen)}
\Ing{2 tbsp ghee, clarified butter, or unsalted butter}
\Ing{8 - 12 oz paneer cheese, cut into 1/2-inch cubes (see p. \pageref{components:paneer})}
\Ing{2 medium onions, finely chopped}
\Ing{Scant \nicefrac{1}{2} tsp fine grain sea salt}
\Ing{3 medium garlic cloves, finely chopped}
\Ing{1 tbsp grated fresh ginger}
\Ing{1 tbsp Saag Paneer Spice Mix (p. \pageref{components:paneer_spice})}
\Ing{\nicefrac{1}{4} tsp ground turmeric}
\Ing{1 cup buttermilk}
\Ing{splash of cream or dollop of plain yogurt (optional)}
\Ing{fresh lemon to finish}

Chop the spinach well, and set aside in a large bowl.\\

While you're chopping spinach, cook the paneer in one tablespoon of the butter over medium heat in a large skillet. Make sure the paneer is in a single layer and use a spatula to flip it regularly so all sides get deeply brown. This typically takes 7 minutes or so. Remove from the pan and set aside.\\

Heat the other tablespoon of butter in your largest soup pot. Add the onions and salt, and saute until the onions soften up, five minutes or so. Add the garlic, ginger, spice mixture, and turmeric. Cook, stirring frequently, until fragrant and nicely combined - a minute or two.\\

Turn the heat up to medium-high and add the spinach to the pan all at once, if possible. Cook, stirring all the while, until the spinach is collapsed and wilted, a couple of minutes. If you need to add the spinach in batches (adding more spinach as it collapses), that is fine too, just do it as quickly as possible.\\

Stir in the buttermilk and cream and heat gently while stirring. If the mixture seems dry, add more buttermilk a splash at a time (this rarely happens to me). Taste and add more salt if necessary and more red pepper flakes if you like. Add a generous squeeze of fresh lemon juice, stir in the paneer and serve.

\end{recipe}