\begin{recipe}{\texorpdfstring{$\star$}{str}Samosa Shepherd's Pie}{6 servings - 432 calories}{}

\freeform From 101 Cookbooks.

\Ing{1 \nicefrac{1}{2} pounds potatoes or sweet potatoes}
\Ing{\nicefrac{2}{3} cup full-fat coconut milk}
\Ing{Fine grain sea salt, to taste\\}
\Ing{1 tbsp coconut oil}
\Ing{1 medium onion, chopped}
\Ing{4 cloves garlic, minced}
\Ing{8 ounces mushrooms, chopped}
\Ing{1 cup crushed tomatoes }
\Ing{2 tsp garam masala}
\Ing{2 cups cooked yellow or green split peas}
\Ing{1 cup peas (fresh or frozen)\\}
\Ing{To serve: chopped serrano chiles, micro greens, scallions}

Place the potatoes/sweet potatoes in a medium saucepan, cover with water, salt as you would pasta water, and bring to a boil for about ten minutes, or until tender. Drain, and return to saucepan over heat for a minute or so to dry out a bit. Add the coconut milk, and the salt, and mash together. Set aside.\\

In a large saucepan over medium-high heat, combine the coconut oil with the onion and garlic, and a generous pinch of salt. Sauté for a few minutes, until onions are translucent, and then turn the heat up and add the mushrooms. Cook, stirring every couple of minutes, until the mushrooms release their water, and start to brown. Add the tomatoes and spices. Stir well, then add the cooked split peas and peas. Cook for another minute or two, taste, and adjust with more garam masala or salt if needed.\\

Transfer the mushroom mixture to a 8-inch baking dish (or equivalent), spreading it across in a somewhat even layer. Dollop the potatoes across the top, and gently push them around until they cover the entire top of the casserole, run the tines of a fork across the top if you like a bit of texture.\\

Bake for 25 minutes, and finish under a broiler to add a bit of extra color and texture to the top. Serve as-is, or sprinkled with any (or all) of the suggested toppings.

\end{recipe}