\begin{recipe}{Stuffed Shells}{4 servings - 622 calories}{}

\freeform From 101 Cookbooks.

\Ing{Zest of one lemon\\}
\Ing{\textbf{Sauce}}
\Ing{\nicefrac{1}{3} cup / 80 ml extra virgin olive oil, plus more for the pan}
\Ing{1 \nicefrac{1}{2} teaspoons crushed red pepper flakes}
\Ing{Scant \nicefrac{3}{4} teaspoon fine grain sea salt}
\Ing{4 medium cloves of garlic, finely chopped}
\Ing{1 28-ounce can crushed red tomatoes}
\Ing{1 14-ounce can crushed red tomatoes\\}
\Ing{\textbf{Filling}}
\Ing{1 15-ounce container ricotta cheese}
\Ing{1 egg, beaten}
\Ing{\nicefrac{1}{4} teaspoon fine grain sea salt}
\Ing{1 cup / \textasciitilde5 oz grated mozzarella}
\Ing{1 bunch of chives, minced\\}
\Ing{28 jumbo dried pasta shells}

Oil a 13 x 9-inch / 33 x 23-cm baking pan, or equivalent, and sprinkle the zest of 1/2 the lemon across it. Set aside. Get a big pot of water boiling, and preheat your oven to 350$\degree$F / 180$\degree$C with a rack in the middle.\\

To make the sauce, combine the olive oil, red pepper flakes, sea salt, and garlic in a cold saucepan. Stir while you heat the saucepan over medium-high heat. Saute just 45 seconds or so until everything is fragrant - you don't want the garlic to brown. Now stir in the tomatoes and heat to a gentle simmer, just a minute or two. Remove from heat and carefully take a taste (you don't want to burn your tongue)...If the sauce needs more salt add it now. Let cool.\\

To make the filling, combine the ricotta, egg, and salt in a medium bowl. Mix until combined, then stir in the mozzarella, remaining lemon zest, and 3/4 of the chives. Set aside.\\

Cook the shells according to package instructions in well-salted water - until al dente. If you overcook, the shells will tear as you attempt to fill them. Drain and let cool long enough to handle with your hands.\\

Spread 1/3 of sauce across the bottom of the prepared pan. Fill each shell with ricotta, and arrange in a single layer in the pan. Ladle the remaining sauce over the shells, cover with foil and bake for 30 minutes, uncover for the final 15 minutes or until the shells are cooked through. Sprinkle with the remaining chives and serve hot.

\end{recipe}