\begin{recipe}{\texorpdfstring{$\star$}{str}Sunshine Pad Thai}{4 servings - 395 calories}{}

\freeform From 101 Cookbooks.

\Ing{6 ounces dried rice noodles}
\Ing{1 \nicefrac{1}{2} tbsp dried turmeric powder}
\Ing{3 tbsp white vinegar}
\Ing{3 tbsp sugar}
\Ing{2 tbsp vegetarian "fish" sauce or soy sauce}
\Ing{2 tbsp oil}
\Ing{1 bunch of broccolini, trimmed}
\Ing{6 ounces extra-firm tofu, crumbled}
\Ing{1 egg}
\Ing{\nicefrac{3}{4} cup bean sprouts or diced celery}
\Ing{\nicefrac{1}{3} cup roasted peanuts}
\Ing{3 green onions, thinly sliced\\}
\Ing{2 limes, cut into wedges}

Fill a large bowl with boiling water, stir in the turmeric, and the noodles. Use a fork to swish them around a bit, and soak until the noodles are pliable and bendy - 5 to 10 minutes. Drain and set aside.\\

In the meantime, whisk together the vinegar, sugar, and soy sauce in a small bowl.\\

Just before you're ready to eat, heat the oil in a wok or large skillet over high heat. Stir in the broccoli, cover, and allow to cook for a few minutes, until the broccolini is bright green, but still al dente. Remove it from the pan, and set aside. Next, add the tofu to the pan, and cook until it begins to brown, a couple of minutes. Add the noodles, and the sauce, and stir constantly until the noodles absorb the sauce - a minute or so.\\

Push the noodles to the side, add the egg, whisk and break it up with the spatula, and allow it to set a bit, 10 or 20 seconds. Break it up, and toss the egg with the noodles. Add the bean sprouts, peanuts, and scallions. Transfer to a large platter and serve topped with the broccolini, and lime wedges.
\end{recipe}