\begin{recipe}{\texorpdfstring{$\star$}{str}Basic Tarka Dal}{6 servings - 129 calories}{}

\freeform From Jamie Oliver.

\Ing{400g red lentils}
\Ing{2 tsp turmeric}
\Ing{2 knobs unsalted butter}
\Ing{2 tsp cumin seeds}
\Ing{1 small onion, finely chopped}
\Ing{2-3 cloves garlic, finely sliced}
\Ing{1-2 fresh green chillies, finely sliced (remove seeds if you want to keep the heat down)\\}
\Ing{1 tsp garam masala}
\Ing{1 tsp ground coriander}
\Ing{thumb-sized piece of fresh ginger, finely grated}
\Ing{2-3 tomatoes, chopped small}

Place the lentils in a pan and cover with enough cold water to come to around two inches above their surface. Bring to the boil (skim off any scum that rises to the top), and reduce to a simmer. Stir in the turmeric and a generous knob of butter. Cover and leave to cook gently.\\

In a small frying pan, dry-fry the cumin seeds over a medium heat until toasted and fragrant (no more than a couple of minutes). Remove from the pan and set to one side.\\

Melt a second knob of butter in the same frying pan and gently fry the chopped garlic, onion, chillies and the grated ginger and tomatoes, if you’re using them. Once the garlic is golden, mix in the toasted cumin seeds and, if using, the garam masala and ground coriander. Remove from the heat until the lentils are completely softened.\\

Give the lentils a good stir. They should have the consistency of porridge – thicker than soup and looser than houmous. Add more water as necessary (you will be surprised how thick they can get over just a couple of extra minutes cooking), and mix in your aromatic fried mixture.\\

Season to taste, then serve on its own, topped with coriander, or with a side of basmati rice and greens.

\end{recipe}