\begin{recipe}{Smoky Tempeh and Hummus Sandwiches}{4 servings - 495 calories}{}

\freeform From {\normalfont Food52 Vegan} by Gena Hamshaw (p. 94).

\Ing{\textbf{Tempeh}}
\Ing{2 tbs. tamari}
\Ing{1 tbs. apple cider vinegar}
\Ing{1 tbs. maple syrup or agave nectar}
\Ing{1 tsp. olive oil}
\Ing{1 tsp. smoked paprika}
\Ing{8 oz (225 g) tempeh, sliced in \nicefrac{1}{4}-in strips\\}
\Ing{\textbf{Hummus}}
\Ing{1 \nicefrac{1}{2} to 2 cups cooked chickpeas}
\Ing{\nicefrac{1}{4} cup tahini}
\Ing{\nicefrac{1}{4} cup freshly squeezed lemon juice}
\Ing{1 clove garlic, minced}
\Ing{\nicefrac{1}{2} tsp. salt}
\Ing{\nicefrac{1}{4} cup water, plus more if needed}
\Ing{\nicefrac{1}{2} tsp. smoked paprika}
\Ing{1 tbs. olive oil\\}
\Ing{8 slices crusty whole grain bread, toasted}
\Ing{1 cup pea shoots}

\textbf{Smoky Tempeh}

Put the tamari, vinegar, maple syrup, olive oil, and paprika in a small bowl or measuring cup and whisk until well blended. Put the tempeh in an 8-in square baking pan. Pour in the marinade and gently turn the tempeh until evenly coated. Cover and refrigerate for 3 to 8 hours.\\

If you'd like to bake the tempeh instead of frying it, preheat the oven to 350$\degree$F. Line a baking sheet with parchment paper. Spread the tempeh on the lined baking sheet and bake for 25 to 30 minutes, flipping the strips halfway through the baking time. Alternatively, heat a few teaspoons of olive oil in a large skillet over medium-high heat and fry the tempeh until golden on both sides.\\

\textbf{Hummus}

Put the chickpeas, tahina, lemon juice, garlic, and salt in a food processor and pulse a few times to combine. With the motor running, drizzle in the water in a thin stream, stopping often to scrape down the sides of the work bowl, until the hummus has a thick and creamy texture that's easy to spread, but not liquidy. Once the texture is to your liking, add the paprika and, with the motor running, drizzle in the olive oil.\\

\textbf{Sandwiches}

For each sandwich, spread \nicefrac{1}{4} to \nicefrac{1}{3} cup of hummus on once slice of bread. Top with 1/4 of the tempeh slices and 1/4 of the pea shoots, then put another slice of bread on top.

\end{recipe}