\begin{recipe}{Tempeh, Lettuce, and Tomato Sandwiches}{4 servings - 610 calories}{}

\freeform From 101 Cookbooks.

\Ing{8 ounces of tempeh, cut into 1/3-inch thick strips}
\Ing{3 tbsp olive oil}
\Ing{\nicefrac{1}{4} cup soy sauce}
\Ing{2 tbsp balsamic vinegar}
\Ing{2 tbsp brown sugar (or maple syrup)}
\Ing{3 tbsp adobo sauce from a can of chipotle peppers\\}
\Ing{1 small basket of cherry tomatoes (2 cups)}
\Ing{\nicefrac{1}{4} cup extra-virgin olive oil olive oil}
\Ing{1 tbsp brown sugar (or maple syrup)}
\Ing{Scant 1/2 tsp of salt\\}
\Ing{1 small head of romaine lettuce, cored, then cut into \nicefrac{1}{4}-inch ribbons}
\Ing{1-2 large avocados, mashed with a pinch of salt just before assembling}
\Ing{4 or 8 extra-thin slices of hearty whole grain bread, well toasted}

Preheat oven to 350F degrees.\\

Whisk together the 3 tablespoons of olive oil, shoyu, balsamic vinegar, brown sugar and adobo sauce. Pour 1/3 of the tempeh marinade into an 8x8 baking dish (or something comparable) - you want a dish that is just big enough to hold the tempeh in a single layer - this way it will be fully enveloped by the marinade. Pour the remaining marinade over the top of the tempeh, cover and keep in the refrigerator for a couple hours, overnight or until ready to use.\\

While the tempeh is marinating, go ahead and roast the tomatoes. Cut each tomato in half and arrange them in a large oven-proof baking dish. Mix together the olive oil, sugar, and salt and pour this over the tomatoes. Gently toss them a bit, making sure they all get coated, finishing with each tomato facing cut-side up. Place in the oven and bake for 45 minutes or so, until the tomatoes are shrunken and sweet.\\

When the tempeh is done marinating heat a large pan over medium-high heat and cook the tempeh slices for a few minutes on each side. You may need to do this in batches if you don't have a big enough pan. Set the tempeh slices aside until you are ready to assemble the sandwiches.\newpage

To assemble each sandwich take one slice of bread and slather a generous layer of mashed avocado. Place a small helping of the shredded lettuce on top of the avocado, a few tomatoes, then a few slices of the tempeh, and more tomatoes. Enjoy either open faced or topped with another avocado-slathered bread slice.

\end{recipe}