\begin{recipe}{$\star$Vegetarian Moussaka}{6 servings - 386 calories}{}

\freeform From {\normalfont The Clueless Vegetarian} by Evelyn Raab (p. 144).

\Ing{2 eggplants}
\Ing{2 tbs. olive oil}
\Ing{1 cup crumbled feta cheese\\}
\Ing{\textbf{Custard}}
\Ing{2 tbs. butter}
\Ing{2 tbs. flour}
\Ing{\nicefrac{3}{4} cup milk}
\Ing{1 tsp. salt}
\Ing{nutmeg and pepper}
\Ing{2 eggs}
\Ing{1 cup ricotta cheese\\}
\Ing{\textbf{Sauce}}
\Ing{2 medium onions, chopped}
\Ing{1 medium zucchini, diced}
\Ing{\nicefrac{1}{2} medium red or green pepper, diced}
\Ing{2 cloves garlic, chopped}
\Ing{2 tbs. olive oil}
\Ing{1 tsp crumbled oregano}
\Ing{\nicefrac{1}{4} tsp. cinnamon}
\Ing{salt and pepper}
\Ing{2 cups diced tomatoes, fresh or canned}
\Ing{3 tbs. tomato paste}

Without peeling them, slice the eggplants into \nicefrac{1}{2}-in thick slices and salt on both sides. Stand them upright (as much as possible) in a colander and allow the liquid to drain for about 30 minutes. Rinse with water, and pat dry. In batches, brush the eggplants slices with the olive oil and broil in a single layer on a baking sheet until lightly browned (about 2 minutes per side), turning them once. Set aside.\\

\textbf{Custard}

Meanwhile, in a saucepan, melt the butter over medium heat. Stir in the milk and cook until smooth and thickened. Remove from heat and stir in the salt, some nutmeg and pepper, the eggs, and ricotta. Set aside.\\

\textbf{Sauce}

In a skillet, cook the chopped, onions, zucchini, pepper, and garlic with the olive oil until softened. Stir in the oregano, cinnamon, salt and pepper, and cook for a minute or so. Add the tomatoes and tomato paste, and simemr the sauce for about 10 minutes, until slightly thickened.\\

\textbf{To Assemble}

Spread half of the tomato sauce in a deep casserole dish, and top with half of the eggplant. Sprinkle with half of the feta cheese, then spread on the rest of the tomato sauce. Layer on the rest of the eggplant, top this with all of the custard, and sprinkle on the rest of the feta cheese.\\

Bake at 350$\degree$F for 50 minutes to 1 hour, until the top is browned and set. Let it stand for about 15 minutes before trying to cut into square.

\end{recipe}