\begin{recipe}{\texorpdfstring{$\star$}{str}Warm Lentil and Potato Salad}{4 servings - 434 calories}{}

\freeform From Smitten Kitchen.

\Ing{2 large shallots, 1 halved, 1 finely diced}
\Ing{4 sprigs of thyme}
\Ing{1 small bay leaf}
\Ing{1 cup dry small green lentils}
\Ing{Salt and pepper}
\Ing{1 pound fingerling potatoes}
\Ing{2 tbsp red wine vinegar}
\Ing{1 to 2 garlic cloves, minced or smashed to a paste}
\Ing{1 tbsp smooth Dijon mustard}
\Ing{\nicefrac{1}{4} cup of your favorite olive oil}
\Ing{2 tsp capers, rinsed if salted, drained if brined, and roughly chopped}
\Ing{2 tbsp cornichons or other sour gherkins, roughly chopped}
\Ing{1 to 2 scallions, thinly sliced}
\Ing{\nicefrac{1}{2} cup cup chopped flat leaf parsley}

Cook lentils: Pick over and rinse lentils. Place them in a small/medium saucepan with the halved shallot, thyme branches, bay leaf, some salt and 4 cups of water. Simmer the lentils over medium heat for 25 to 30 minutes, until firm-tender. Drain (discarding shallot, thyme and bay leaf) and keep warm.\\

Meanwhile, cook potatoes: In a separate saucepan, cover potatoes with 1 to 2 inches cold water. Set timer for 15 minutes, then bring potatoes to a simmer. When the timer rings, they should be easily pierced with a toothpick or knife. Drain and keep warm.\\

Make the dressing: Place the chopped shallot and red wine vinegar in the bottom of a small bowl and let sit for 5 minutes. Whisk in minced garlic, dijon, a pinch of salt, a few grinds of black pepper and olive oil. Stir in chopped capers, cornichon and scallions.\\

Assemble salad: Slice potatoes into 1/2-inch segments and place in serving bowl. Add lentils, dressing and all but 1 tablespoon parsley and combine. Adjust seasoning with additional salt and pepper if needed. Scatter salad with remaining parsley.

\end{recipe}