\begin{recipe}{Whole Lemon Bars}{9 bars - 305 calories ea.}{}

\freeform From David Lebovitz.

\Ing{\textbf{Crust}}
\Ing{1 cup (140g) flour}
\Ing{\nicefrac{1}{4} cup (50g) sugar}
\Ing{\nicefrac{1}{4} teaspoon salt}
\Ing{8 tablespoons (115g) melted unsalted butter}
\Ing{\nicefrac{1}{2} teaspoon vanilla extract\\}
\Ing{\textbf{Lemon Topping}}
\Ing{1 lemon, organic or unsprayed}
\Ing{1 cup (200g) sugar}
\Ing{3 tablespoons (45ml) freshly squeezed lemon juice}
\Ing{3 large eggs, room temperature}
\Ing{4 teaspoons corn starch}
\Ing{\nicefrac{1}{4} teaspoon salt}
\Ing{3 tablespoons (45g) melted unsalted butter}
\Ing{Optional: powdered sugar, for serving}

Preheat the oven to 350ºF (180ºC).\\

Overturn an 8-inch square pan on the counter and wrap the outside snugly with foil, shiny side up. Remove the foil, turn the pan over, and fit the foil into the pan, pressing to nudge the foil into the corners. Then smooth it as best you can. Lightly butter or spray the surface of the foil with nonstick spray.\\

In a medium bowl, mix the flour, 1/4 cup (50g) sugar, 1/4 teaspoon salt, 8 tablespoons (115g) melted butter, and vanilla, stirring just until smooth.\\

Smooth the batter into the bottom of the pan, using your hands or a small offset spatula to get it as level as possible.\\

Bake the crust for 25 minutes, or until it’s deep-golden brown.\\

While the crust is cooking, cut the lemon in half, remove the seeds, and cut the lemon into chunks.\\

Put the chunks of lemon in a food processor or blender along with the sugar and lemon juice, and let it run until the lemon is completely broken up. Add the eggs, corn starch, 1/4 teaspoon of salt, and 3 tablespoons (45g) melted butter, and blend until almost smooth. (A few tiny bits of lemon pieces are normal and encouraged).\\

When the crust comes out of the oven, reduce the heat of the oven to 300$\degree$F (150$\degree$C). Pour the lemon filling over the hot crust and bake for 25 minutes or just until the filling stops jiggling and is barely set.\newpage

Remove from the oven and let cool completely. Once cool, carefully lift out the bars grasping the foil. Cut the bars into squares or rectangles. Sift powdered sugar over the top just before serving, if desired.\\

The bars will keep in an airtight container at room temperature up to three days. You can freeze the lemon bars as well for up to one month, letting them come to room temperature before serving.

\end{recipe}