\begin{recipe}{\texorpdfstring{$\star$}{str}Fried Rice with Zucchini, Tomatoes and Parmesan}{4 servings - 386 calories}{}

\freeform From Smitten Kitchen.

\Ing{Olive oil}
\Ing{1 medium-large sweet onion, diced or 1/2 a large onion}
\Ing{Salt and freshly ground black pepper, plus red pepper flakes for heat if desired}
\Ing{3 garlic cloves, minced}
\Ing{1 pound zucchini or other summer squash (about 2 small/medium), diced}
\Ing{1 tsp finely chopped fresh thyme leaves}
\Ing{\nicefrac{1}{2} cup small red cherry or grape tomatoes, sliced \nicefrac{1}{4}-inch thick if large, halved if tiny}
\Ing{2\nicefrac{1}{2} to 3 cups cooked, ideally day old, short-grain white or brown rice}
\Ing{\nicefrac{1}{2} cup grated Parmesan, divided}
\Ing{Handful chopped flat-leaf parsley}
\Ing{2 large eggs}

Heat a large, heavy frying pan to medium-high heat. Once hot, add 1 tablespoon oil, then onion and cook, stirring, for 5 to 10 minutes, until quite browned at edges. Season well with salt and pepper. Add garlic and cook 1 minute more. Scrape onion and garlic into a bowl.\\

Add another tablespoon oil to pan. Add zucchini and spread evenly in pan. Season well with salt and pepper and cook, not stirring at all, until beginning to blister in brown spots underneath, about 3 to 5 minutes. Stir and flip zucchini, then add thyme, and cook for 3 to 5 minutes more, until there are browned spots throughout. Add tomatoes and cook for 2 to 3 minutes. Scrape zucchini and tomatoes into a bowl\\

Add another glug of oil to the pan and add rice, pressing it in one layer. Cook until beginning to brown and crisp underneath, about 5 to 7 minutes. Give it a stir, season it well with salt and pepper, and repeat the press-and-crisp process for a few more minutes. Return onion/garlic and zucchini/tomatoes to pan and cook together for one minute. Stir in half of Parmesan and parsley.\\

Push the fried rice to the side and crack eggs directly into the cleared area. Use a fork or spatula to break them up and half-scramble them (I like them a little unmixed) in the pan, then stir the chopped scramble back into the fried rice. Serve with remaining Parmesan on top.

\end{recipe}