\begin{recipe}{Crispy Home Fries With Red Onions}{4 servings - 293 calories}{}

\freeform From Serious Eats.

\Ing{1 \nicefrac{1}{4} pounds (575g) small new or fingerling potatoes}
\Ing{Kosher salt}
\Ing{1 tablespoon (15ml) distilled white vinegar}
\Ing{\nicefrac{1}{4} cup (60ml) vegetable oil, divided}
\Ing{1 small red onion, cut into thick slices}
\Ing{2 teaspoons (about 4g) minced fresh thyme}
\Ing{Freshly ground black pepper}
\Ing{Small handful minced fresh cilantro or parsley}

Place potatoes in a pot and cover with 2 quarts (2L) of cold water. Add 2 tablespoons (30g) kosher salt and vinegar. Bring to a boil over high heat and boil until potatoes are tender, about 5 minutes after they reach a boil. Drain. As soon as potatoes are cool enough to handle, split into quarters and toss with 1 tablespoon (15ml) vegetable oil in a bowl.\\

Heat 2 tablespoons (30ml) vegetable oil in a large nonstick or cast iron skillet over medium-high heat until shimmering. Add potatoes and cook, tossing, until crisp and golden brown on all sides, about 6 minutes. Return to bowl.\\

Add remaining tablespoon (15ml) oil to skillet and add red onion. Cook, tossing occasionally, until softened and lightly browned, about 6 minutes. Add thyme and cook, stirring, until fragrant, about 30 seconds. Return potatoes to skillet. Toss to combine and season to taste with plenty of salt and pepper. Add cilantro or parsley and toss to combine. Serve immediately.\\

\textbf{Notes:}

To prepare potatoes ahead of time, store the parboiled potatoes in the refrigerator for up to 3 days before continuing.

\end{recipe}