\begin{recipe}{$\star$Green Lentil Soup with Cumin and Lemon}{6 servings - 224 calories}{}

\freeform From {\normalfont Love Soup} by Anna Thomas (p.134).

\Ing{1 cup / 8 oz / 225 g French (Le Puy) green lentils}
\Ing{1 \nicefrac{1}{2} tsp. sea salt, plus more to taste}
\Ing{2 tbs. olive oil}
\Ing{1 large yellow onion, chopped}
\Ing{2 cups chopped leeks, white and light green parts}
\Ing{1 medium sweet potato, diced}
\Ing{1 large carrot, finely diced}
\Ing{1 large celery stalk, finely diced}
\Ing{1 bay leaf}
\Ing{1 bunch green chard}
\Ing{2 tbs. cumin seeds}
\Ing{1 cup chopped cilantro}
\Ing{\nicefrac{1}{4} cup chopped fresh flat-leaf parsley}
\Ing{Cayenne pepper, to taste}
\Ing{2-3 cups vegetable broth}
\Ing{1-2 tbs. fresh lemon juice, plus more to taste}

Rinse the lentils and combine them in a large soup pot with 4 cups water. Bring the water to a boil, then lower the heat and simmer the lentils gently for about 25 minutes, or until tender-firm. After the first 20 minutes, add as teaspoon of sea salt, and when the lentils are ready, remove them from the heat and skim off any foam that may have formed on top.\\

Meanwhile, heat 2 tablespoons olive oil in a large sauté pan, add the chopped onion and a pinch of sea salt, and cook slowly over medium heat until the onion is soft, 8 to 10 minutes. Add the leeks and continue cooking for another 20 minutes, stirring often, until the leeks and onion are translucent and turning golden.\\

Add the onion and leeks to the lentils and their broth, along with the diced sweet potato, carrot, celery, another 3 cups water, half a teaspoon of sea salt, and the bay leaf. Simmer the soup gently, covered, for about 20 minutes. Meanwhile, wash the chard, slice away the stems, and coarsely chop the green leaves. Add the chard and simmer the soup another 10 minutes, until the vegetables are all tender.\newpage

Lightly toast the cumin seeds in a dry skillet, just until they release their fragrance, about 4 to 5 minutes, then grind them in a mortar or spice grinder and stir them into the soup. Add the cilantro and parsley,a generous pinch of cayenne. and 2 or 3 cups of light vegetable broth, enough to give the soup the consistency you like. I like my soups to pour easily from the ladle. Heat everything together for a few more minutes, then add lemon juice to taste.\\

Serve the soup steaming hot in wide bowls and drizzle some olive oil over each serving.

\end{recipe}