\begin{recipe}{Red Curry Peanut Zoodles}{6 servings - 531 calories}{}

\freeform From Cupcakes and Kale (modified slightly).

\Ing{1 can coconut milk}
\Ing{\nicefrac{1}{4} cup natural peanut butter}
\Ing{2-3 tbsp Thai red curry paste}
\Ing{2 tbsp tamari}
\Ing{\nicefrac{1}{2} lime, juiced}
\Ing{\nicefrac{1}{2} tbsp brown sugar}
\Ing{1 tsp toasted sesame oil}
\Ing{2 tsp minced fresh ginger}
\Ing{2 cups broccoli florrets}
\Ing{1 cup sliced carrots}
\Ing{1 \nicefrac{1}{2} cups sugar snap peas}
\Ing{1 zucchini, spiralized}
\Ing{400 g udon noodles}
\Ing{chopped roasted peanuts, to garnish}
\Ing{chopped cilantro, to garnish}
\Ing{1 block extra firm dry-fried tofu, to garnish}

In a small saucepan, combine the coconut milk, peanut butter, curry paste, tamari, lime juice and brown sugar. Simmer gently over medium-low heat for 5-10 minutes whisking periodically. Taste and adjust flavours to suit your preference. I sometimes like a bit more tamari.\\

Cook the udon noodles according to the package directions and set aside.\\

While sauce is simmering, heat the sesame oil and ginger in a large skillet over medium-high heat. Add the broccoli and carrots and sauté 2-3 minutes while stirring. Add the peas and continue to cook another minute or two. The vegetables should be bright and vibrant and still hold the better part of their crunch.\\

To serve, fill bowls with a combination of rice noodles and zucchini noodles. Ladle over the hot curry sauce and top with the vegetables. Serve garnished with chopped peanuts and cilantro.

\end{recipe}