\begin{recipe}{$\star$Rustic Leek and Potato Soup}{6 servings - 226 calories}{}

\freeform From {\normalfont Love Soup} by Anna Thomas (p.158).

\Ing{3-4 large leeks, white and light green parts}
\Ing{2 lbs. Yukon Gold potatoes}
\Ing{1 tbs. olive oil}
\Ing{1 tbs. unsalted butter}
\Ing{1 \nicefrac{1}{2} tsp. sea salt, plus more to taste}
\Ing{3 cups vegetable broth}
\Ing{3 tbs. chopped fresh flat-leaf parsley}
\Ing{\nicefrac{1}{2} tsp. chopped fresh thyme}
\Ing{Freshly ground black pepper}
\Ing{2 tsp. fresh lemon juice}
\Ing{3 tbs. heavy cream\\}
\Ing{Chopped parsley or snipped chives for garnish}

Trim the leeks and wash them well, slice them in quarters lengthwise, then slice them crosswise; you should have 3 to 3 \nicefrac{1}{2} cups. Scrub the potatoes and cut them into \nicefrac{1}{2}-inch dice.\\

Heat the olive oil and butter in a skillet, add the leeks and a pinch of salt, and cook the leeks over medium heat, stirring often, until they are soft and just beginning to colour, 8 to 10 minutes.\\

Combine the leeks and potatoes into a large soup pot with 3 cups water, a teaspoon of sea salt, and the vegetable broth and simmer, covered, for about 15 minutes, or until the potatoes are completely tender. Add the parsley and thyme, some black pepper, and the lemon juice. Taste and correct the seasoning with more salt if needed; potatoes absorb quite a lot of salt, but wait a moment between additions, as salt needs time to dissolve.\\

Stir in the cream and serve with more fresh parsley or chopped chives sprinkled on top.

\end{recipe}