\begin{recipe}{Southwest Potatoes}{4 servings - 638 calories}{}

\freeform From New York Times Cooking, by Mark Bittman. Also good for brunch.

\Ing{5 tablespoons olive oil, or more as needed}
\Ing{2 tablespoons minced fresh jalapeño, or to taste}
\Ing{1 to 1 \nicefrac{1}{2} cups corn kernels, fresh or frozen}
\Ing{Salt}
\Ing{Black pepper}
\Ing{2 pounds new potatoes, peeled and cut into 1-inch chunks}
\Ing{\nicefrac{1}{2} to 1 teaspoon chili powder, or to taste}
\Ing{1 14-ounce can black beans, well drained}
\Ing{\nicefrac{3}{4} to 1 cup grated Cheddar or jack cheese}
\Ing{\nicefrac{1}{2} cup chopped fresh cilantro, for garnish}

Put 1 tablespoon of oil in a large skillet over medium heat. When hot, add jalapeño and corn, and sprinkle with salt and pepper; let sit for a moment. When corn begins to brown, shake pan to distribute for even browning. Remove corn.\\

Add remaining oil to pan. When hot, add potatoes. Cook, undisturbed, until they begin to brown around edges and release from pan, about 10 minutes. Continue, at least 15 more minutes, turning potatoes to brown all sides without stirring too often. Add oil if needed to prevent sticking, and lower heat if needed to prevent scorching. When potatoes are tender and golden, add chili powder, corn and beans.\\

Turn on broiler. Place rack about 4 inches below. Transfer potatoes to a baking dish, sprinkle with cheese and run under broiler until cheese is melted and beginning to brown, 2 to 3 minutes. Garnish with cilantro.

\end{recipe}