\begin{recipe}{$\star$Tempeh Taco Salad}{4 servings - 410 calories}{}

\freeform From 101 Cookbooks.

\Ing{2 teaspoons extra virgin coconut or olive oil}
\Ing{8 ounces tempeh}
\Ing{1 tablespoon taco seasoning\\}
\Ing{\nicefrac{1}{3} cup ketchup}
\Ing{\nicefrac{1}{2} cup apple cider vinegar}
\Ing{2 tablespoons coconut nectar, maple syrup, or honey}
\Ing{\nicefrac{1}{4} teaspoon salt}
\Ing{1 \nicefrac{1}{2} teaspoons smoked paprika}
\Ing{1 teaspoon onion powder}
\Ing{\nicefrac{1}{3} cup organic sunflower oil\\}
\Ing{1 14-ounce can black beans, drained and rinsed}
\Ing{15 black olives, chopped}
\Ing{\nicefrac{1}{2} cup sliced green onions}
\Ing{2 medium heads of romaine lettuce, sliced}
\Ing{1 cup cilantro, chopped}
\Ing{1 - 2 cups tortilla chips}
\Ing{1 avocado, sliced\\}
\Ing{to serve, optional; cherry tomatoes, roasted cherry tomatoes, lime, pickled red onions}

In a large skillet over medium high heat combine the oil and tempeh, and cook, until browned. Transfer to a large serving bowl, add the taco seasoning, and stir well. Allow to cool for a bit while you make the dressing.\\

Combine the ketchup, apple cider vinegar, sweetener, salt, smoked paprika, onion powder, and oil in a jar. Close with a lid, and shake vigorously until creamy and emulsified. Alternately, you can use a blender or hand blender.\\

Just before serving, add the beans, and black olives to the tempeh mixture, drizzle generously with some of the dressing, and toss well. Add the green onions, lettuce, cilantro, chips, avocado, and more dressing, if you like, and gently toss again. Serve as-is, or topped with a squeeze of lime, some tomatoes, more avocado, and green onions, and herbs.

\end{recipe}