\begin{recipe}{Vegan Chocolate Chip Cookies}{16 cookies - 220 calories ea.}{}

\freeform From Cupcakes and Kale.

\Ing{\nicefrac{1}{2} cup (vegan) butter, softened}
\Ing{\nicefrac{3}{4} cup + 2 tbsp packed brown sugar}
\Ing{\nicefrac{1}{4} cup unrefined cane sugar}
\Ing{4 tbsp aquafaba}
\Ing{1 tsp real vanilla extract}
\Ing{\nicefrac{3}{4} tsp baking soda}
\Ing{\nicefrac{1}{4} tsp fine pink Himalayan sea salt (or equivalent)}
\Ing{1 \nicefrac{3}{4} cups all purpose flour}
\Ing{1 heaping cup semi-sweet chocolate chunks or chopped 65-70\% chocolate bar}
\Ing{Flaked sea salt, to finish (optional)}

Preheat the oven to 360$\degree$F.\\

In a large bowl, cream together the vegan butter and sugars until fluffy, about 4-5 minutes. This can be done by hand (look out, it's a workout!) or with an electric mixer or in a stand mixer.\\

Add in the aquafaba and vanilla and mix another 2 minutes.\\

Stir in the baking soda and salt until combined, followed by the flour until just mixed.\\

Using a sharp knife, roughly chop about half of the chocolate chunks. If using a chocolate bar, chop into \nicefrac{1}{2}-in chunks. Fold in the chocolate, crumbs and all by hand.\\

Line a baking sheet with parchment paper or a silpat. Using a small ice cream scoop, scoop about 1.5-2 tablespoons worth of cookie dough and transfer to the baking sheet, leaving about 2 inches between cookies. Sprinkle with flaked sea salt.\\

Bake for 11 minutes, remove to cool 5 minutes on the baking sheet, then transfer to a wire rack.\\

\textbf{Notes}

Cooled cookies can be reheated to achieve the melted chocolate goodness again by placing in a hot oven for a minute or two.\\

Can use aquafaba from a can of black beans, chickpea aquafaba, or great northern bean aquafaba.

\end{recipe}